\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-17 k-planar.tex
Fixed wording

\begin{lem}
	\label{induction} The setup:
	\begin{compactenum}
		\item Let $G$ be a $d$-framed multigraph and let $G'$ be a frame of $G$.
		\item Let $F_0$ be the outer face of $G'$ and let $T$ be a BFS spanning forest of $G'$ rooted at $V(F_0)$.
		\item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
		\item Let $F$ be a cycle in $G'$ that $V(F)$ is partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
		\begin{compactenum}
			\item $F[P_i]$ is connected; and
			\item $P_i=Y_i\cup X_i$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
		\end{compactenum}
		\item Let $N$ and $N'$ be the subgraphs of $G$ and $G'$ consisting only of those edges and vertices contained in the closure of $F$.
	\end{compactenum}
	Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
	\begin{compactenum}[(i)]
		\item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
		\item For each $x\in V(H)$, $S_x=Y_x\cup X_x$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
		\item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$, then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
	\end{compactenum}
\end{lem}

>>>>

\note{PM}{I've changed my mind about this notation change.  We end up applying the lemma inductively on the faces $F_1,\ldots,F_m$ of $M$ (which are cycles in $G$).  It makes sense that the original cycle in $G$ is called $F$.}

\begin{lem}
  \label{induction} The setup:
  \begin{compactenum}
    \item Let $G$ be a $d$-framed multigraph and let $G'$ be a frame of $G$.
    \item Let $F_0$ be the outer face of $G'$ and let $T$ be a BFS spanning forest of $G'$ rooted at $V(F_0)$.
    \item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
    \item Let $F$ be a cycle in $G'$ whose vertices are partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
    \begin{compactenum}
      \item $F[P_i]$ is connected; and
      \item $P_i=Y_i\cup X_i$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
    \end{compactenum}
    \item Let $N$ and $N'$ be the subgraphs of $G$ and $G'$ consisting only of those edges and vertices contained in the closure of $F$.
  \end{compactenum}
  Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
  \begin{compactenum}[(i)]
    \item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
    \item For each $x\in V(H)$, $S_x=Y_x\cup X_x$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
    \item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$, then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
  \end{compactenum}
\end{lem}
